Fasano Franceschini Test: an Implementation of a 2-Dimensional Kolmogorov--Smirnov in \proglang{R}

### 2020-12-23 journalMS/article.tex
updated ff algorithm figure
added figure for issue with 2d CDF

Similar to the 1-D KS test, the obvious solution to extend the theory into higher dimensional would be to define the maximal cumulative difference between the two 2-D distributions. This however, presents an issue as the commutative distribution function is not well defined in more than one dimension. In N dimensional space there are $2^{N}-1$ independant ways of defining the cumlative distribution function\citep{Peacock1983}.

ADD FIGURE for showing the 4 ways (3 independent ways) of defining the cummaltive distribution in 2-D.
$P(x < X, y < Y) = 1 - P(x > X, y > Y); P(x < X, y > Y); P(x > X, y < Y)$

@@

The algorithm loops through each point in the orange sample in turn to define the origin of 4 quadrants (grey dotted line). The fraction of orange and blue points in each quadrant is computed (corners of plot) and the quadrant with the maximal difference is designated the current maximum for the specified origin. By ranging over all pairs of data points and quadrants, the 2-D D-stat is defined by the maximal difference of the integrated probabilities between samples. In this case using the orange point as the origin, the maximal difference is $D = 0.35$.

>>>>

Similar to the 1-D KS test, the obvious solution to extend the theory into higher dimensional would be to define the maximal cumulative difference between the two 2-D distributions. This however, presents an issue as the commutative distribution function is not well defined in more than one dimension. In 2-D, there are 4 ways (3 independent ways) of defining the cummaltive distribution (\textbf{Figure \ref{fig:kstest2Dissue}}). In N dimensional space there are $2^{N}-1$ independant ways of defining the cumlative distribution function\citep{Peacock1983}.

\begin{figure}[t!]
\centering
\includegraphics{CDF2Dissue}
\caption{\label{fig:kstest2Dissue} 4 ways (3 independent ways) of defining the cummaltive distribution for a given point in 2-D.
$P(x < X, y < Y) = 1 - P(x > X, y > Y); P(x < X, y > Y); P(x > X, y < Y)$}
\end{figure}

@@

The algorithm loops through each point in the orange sample in turn to define the origin of 4 quadrants (grey dotted line). The fraction of orange and blue points in each quadrant is computed (corners of plot) and the quadrant with the maximal difference is designated the current maximum for the specified origin. By ranging over all pairs of data points and quadrants, the 2-D D-stat is defined by the maximal difference of the integrated probabilities between samples. In this case using the orange point as the origin, the maximal difference is $D = 0.60$.
